---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regexcite

<!-- badges: start -->
<!-- badges: end -->

The goal of regexcite is to make regular expressions more exciting! It provides convenience functions to make some common tasks with string manipulation and regular expressions a bit easier.

## Installation

You can install the development version of regexcite from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("nshack99/regexcite")
```

## Example

A common task when dealing with strings is splitting a single string into many parts:
```{r example}
library(regexcite)

x <- "alfa,bravo,charlie,delta"
str_split_one(x, pattern = ",")
```

You can also use the `n` argument to limit the number of splits:
```{r}
str_split_one(x, pattern = ",", n = 2)
```